A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-08-22 paper/paper.tex
paper: some diagrams for DeltaHat
tab-coh: fix the proof term of coh_layer
tab-coh: MAJ
paper: put the q back into restr
tab-coh: add brackets around ap

\newcommandx{\cohtwo}[9][2,3,4,5,6,7,8,9]{
  \ensuremath{\mathsf{\color{chestnut}{coh2}}_{
    \mathsf{\color{indian-yellow}{#1}}
    \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
  \setkeys*[bonak]{coh#1}{#9}
}

@@

% Some abbreviations
\newcommand{\imp}{\rightarrow}
\newcommand{\overright}[1]{\overrightarrow{#1}}
\renewcommand{\D}{D}
\newcommand{\hdD}{D.1}
\newcommand{\tlD}{D.2}
\renewcommand{\d}{d}
\newcommand{\E}{E}
\renewcommand{\l}{l}
\renewcommand{\c}{c}
\newcommand{\pair}[2]{#1, #2}

@@

Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT. The most significant implementation of cubical type theory in the real world is an branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}. Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.

@@

\section{Mathematical treatment of \texorpdfstring{$\nu$}{nu}-sets}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{semi-simplicial} sets, and semi-cubical sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies. Since they're not of particular interest, and indeed, we plan to extend our work to do degeneracies in the future, we briefly explain the mathematical objects we have formalized.

@@

@@

  $$
    \begin{tikzcd}
      0 \arrow[r, dash] & 1
    \end{tikzcd}
  $$

@@

  $$
    \begin{tikzcd}
      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
    \end{tikzcd}
  $$
\end{example}

@@

% Restriction for frame, layer, and filler
% Drop the unviverse letter and q
\newcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][][#4][#5][#6][#7]}

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\newcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}

>>>>

\newcommandx{\cohtwo}[9][2,3,4,5,6,7,8,9]{
  \ensuremath{\mathsf{\color{chestnut}{coh2}}_{
    \mathsf{\color{indian-yellow}{#1}}
    \joinargs{,}[#2][#3][#4][#5][#6][#7]}^{\joinargs{}[#8]}}
  \setkeys*[bonak]{coh#1}{#9}
}

@@

% Some abbreviations
\newcommand{\imp}{\rightarrow}
\newcommand{\overright}[1]{\overrightarrow{#1}}
\renewcommand{\D}{D}
\newcommand{\hdD}{D.1}
\newcommand{\tlD}{D.2}
\renewcommand{\d}{d}
\newcommand{\E}{E}
\newcommand{\ap}{\mathsf{ap}}
\renewcommand{\l}{l}
\renewcommand{\c}{c}
\newcommand{\pair}[2]{#1, #2}

@@

Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT. The most significant implementation of cubical type theory in the real world is a branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}. Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.

@@

\section{Mathematical treatment of \texorpdfstring{$\nu$}{𝜈}-sets}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{semi-simplicial} sets, and semi-cubical sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies. Since they're not of particular interest, and indeed, we plan to extend our work to do degeneracies in the future, we briefly explain the mathematical objects we have formalized.

@@

\begin{example}[$\DeltaHat^0$, $\DeltaHat^1$, $\DeltaHat^2$]
  $\DeltaHat^0$ can be drawn as:
  \begin{equation*}
    \begin{tikzcd}
      \bullet
    \end{tikzcd}
  \end{equation*}

  $\DeltaHat^1$ can be drawn as:
  \begin{equation*}
    \begin{tikzcd}
      \bullet \arrow[r, dash] & \bullet
    \end{tikzcd}
  \end{equation*}

  $\DeltaHat^2$ can be drawn as:
  \begin{equation*}
    \begin{tikzcd}
      & \bullet\arrow[dr, dash] & \\
      \bullet\arrow[rr, dash]\arrow[ur, dash] && \bullet
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, dash] & 1
    \end{tikzcd}
  \end{equation*}

@@

  \begin{equation*}
    \begin{tikzcd}
      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

% Restriction for frame, layer, and filler
% Drop the unviverse letter
\newcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\newcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
